\hypertarget{index_intro_sec}{}\section{Introduction}\label{index_intro_sec}
This a custom R\+O\+O\+T library that provides a framework for physics analysis. It contains several functions and classes that aid in analyzing high energy physics data. To aid in the compilation of all the source code, a macro entitled {\ttfamily Compile\+Source.\+C} can be executed from the command line. All functions and classes are available in python from the {\ttfamily lib/\+H\+A\+L.\+py} module. Furthermore, everything lives in the '\hyperlink{namespace_h_a_l}{H\+A\+L}' namespace. \hyperlink{namespace_h_a_l}{H\+A\+L} stands for~\newline
H -\/ H.\+E.\+P.~\newline
A -\/ Analysis~\newline
L -\/ Library~\newline
Of course, this is also a thinly veiled reference to the villian in the classic \char`\"{}2001\+: A Space Odyssey.\char`\"{} However, this bit of software is far less pernicious.\hypertarget{index_overview_sec}{}\section{Overview}\label{index_overview_sec}
\hyperlink{namespace_h_a_l}{H\+A\+L}'s design goals are\+:~\newline
Flexiblity -\/ Users have choice in how they use \hyperlink{namespace_h_a_l}{H\+A\+L}. A user can take full advantage of the builtin framework and wide selection of generic algorithms or just add a few helpful \hyperlink{namespace_h_a_l}{H\+A\+L} classes or functions to an existing analysis.~\newline
Usability -\/ \hyperlink{namespace_h_a_l}{H\+A\+L} strives to make the user experience as physics-\/focused as possible. This means providing classes that do a lot of the heavy lifting, including\+: reading a T\+Tree and assigning branches, looping over events, making unique tuples from lists of particles, and more. The interfaces for these classes are designed for a smooth user experience.~\newline
Extensibility -\/ The framework in \hyperlink{namespace_h_a_l}{H\+A\+L} is trivially extended with custom user code. This means that analysis-\/specific code can couple with generic algorithms with minimal effort.~\newline
Performance -\/ \hyperlink{namespace_h_a_l}{H\+A\+L} leverages the performance advanages of C++. The framework is competitive with hand-\/coded analyses but with advanage of ample code reuse.~\newline
